### 2015-08-12 writing/SNLI paper/corpus.tex
Clarify coref para

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label (\citealt{de2008finding} $\S4.3$; \citealt{marelli2014sick}). 
For instance, the sentence pair \word{A boat sank in the Pacific Ocean} and \word{A boat sank in the Atlantic Ocean} could be labeled as a contradiction if the annotator assumes that the two events under discussion are coreferent, but could also be reasonably labeled as neutral if that assumption is not made. For a similar case with potentially different inutitions, \ii{Ruth Bader Ginsburg was appointed to the US Supreme Court} and \ii{I had a sandwich for lunch today} could be labeled as neutral if the annotator allows that they need not be refer to the same event, but is necessarily a contradiction if the annotator takes coreference to be required. Entity coreference presents a similar kind of uncertainty, as in the pair \word{A tourist visited New York} and \word{A tourist visited the city}. Assuming coreference between \ii{New York} and \ii{the city} justifies labeling the pair as an entailment, but without that assumption \ii{the city} could be taken to refer to a specific unknown city, leaving the pair neutral.

>>>>

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label (\citealt{de2008finding} $\S4.3$; \citealt{marelli2014sick}). 
For instance, the sentence pair \word{A boat sank in the Pacific Ocean} and \word{A boat sank in the Atlantic Ocean} could be labeled as a contradiction if the annotator assumes that the two events under discussion are coreferent, but could also be reasonably labeled as neutral if that assumption is not made. In order to ensure that our labeling scheme is consistent across annotators, we need to select one of these approaches, but there are pitfalls to both choices. If we instruct annotators not to assume that entities are coreferent, than we will only ever see contradictions between sentences that make broad universal assertions, but if we instruct them to always assume coreference, other problems emerge. 
For a similar example with potentially different inutitions, \ii{Ruth Bader Ginsburg was appointed to the US Supreme Court} and \ii{I had a sandwich for lunch today} would be labeled as neutral if the annotator allows that they need not be refer to the same event, but is unintuitively a contradiction if we require that events corefer.

Entity coreference presents a similar kind of uncertainty, as in the pair \word{A tourist visited New York} and \word{A tourist visited the city}. Assuming coreference between \ii{New York} and \ii{the city} justifies labeling the pair as an entailment, but without that assumption \ii{the city} could be taken to refer to a specific unknown city, leaving the pair neutral. This kind of indeterminacy can be resolved only once the questions of coreference are resolved.
